### 2020-06-11 writeup/app_exp.tex
F.1
sec F

\subsection{Synthetic Settings}\label{app_synthetic}
	We describe the parameters used for producing Figure \ref{fig_model_shift_phasetrans}.
	For all three simulations, we use dimension $p = 200$.
	In Figure \ref{fig_model_shift}, we use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measure the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	In Figure \ref{fig_size}, we set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
	In Figure \ref{fig_covariate}, we set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

@@

\iffalse
\textbf{Further results on covariance alignment.}
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance. We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
	\label{fig_covariate_app}
\end{figure}
\fi

>>>>

\subsection{Synthetic Settings}\label{app_synthetic}
	We describe the parameters used for producing Figure \ref{fig_model_shift_phasetrans}.
	For all three simulations, we use dimension $p = 200$.
	In Figure \ref{fig_model_shift}, we use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measure the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	In Figure \ref{fig_size}, we set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
	In Figure \ref{fig_covariate}, we set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
	This can be achieved similarly by rescaling the task data.

@@

\textbf{Further results on covariance alignment.}
Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
One possible explanation is overfitting because of additional parameters from the alignment module.
It would be interesting to understand when adding the alignment module provides benefit to the multi-task learning model.
We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance. We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
	\label{fig_covariate_app}
\end{figure}
